%-------------------------
% Resume in Latex
% Author : Aras Gungore
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome5}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}
\setlength{\footskip}{8pt}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeRoleHeading}[2]{
    \vspace{2pt}
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeCompanyHeading}[2]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-2pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabularx}{0.97\textwidth}{@{}Xr@{}}
      \small #1 & \small #2 \\
    \end{tabularx}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \par\vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}\par
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Taha Binhuraib} \\ \vspace{3pt}
    \small Ph.D. researcher in language and brain modeling with active publications and prior leadership in production LLM systems. \\ \vspace{4pt}
    \small
    \faIcon{at} \hspace{.5pt} \href{mailto:taha.huraib@gmail.com}{taha.huraib@gmail.com}
    $|$
    \faIcon{linkedin} \hspace{.5pt} \href{https://www.linkedin.com/in/tahabinhuraib/}{LinkedIn}
    $|$
    \faIcon{github} \hspace{.5pt} \href{https://github.com/TahaBinhuraib}{GitHub}
    $|$
    \faIcon{globe} \hspace{.5pt} \href{https://scholar.google.com/citations?user=BLCXvnYAAAAJ&hl=en}{Google Scholar}
    $|$
    \faIcon{map-marker-alt} \hspace{.5pt} Atlanta, GA
\end{center}


%----------- EDUCATION -----------

\section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
      {Georgia Institute of Technology}{GA, USA}
      {Ph.D. in Cognition and Brain Sciences}{2024 -- Present}
    \resumeSubheading
      {Bahcesehir University}{Istanbul, Turkey}
      {B.Sc. in Industrial Engineering; \textbf{GPA: 3.80/4.00}}{2017 -- 2021}
      
      Graduated with high honors as the second-ranking student in the department.

  \resumeSubHeadingListEnd

%----------- RESEARCH EXPERIENCE -----------

\section{Research Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Language, Intelligence and Thought (LIT) Lab, Georgia Tech}{Atlanta, GA}
      {Ph.D. Student, advised by Anna Ivanova}{2024 -- Present}
        \resumeItemListStart
            \resumeItem{Study the intersection of language processing in the brain and neural networks, focusing on interpretable encoding models that map language to brain activity.}
            \resumeItem{Investigate topographic language models and brain-like spatial organization in artificial neural networks.}
        \resumeItemListEnd

    \resumeSubheading
      {Vision Lab, Istanbul Technical University}{Istanbul, Turkey}
      {Research Assistant}{Mar 2023 -- Present}
        \resumeItemListStart
            \resumeItem{Conducted research in deep generative modeling and co-authored \emph{Protodiffusion: classifier-free diffusion guidance with prototype learning} (ACML 2023).}
            \resumeItem{Developed and evaluated prototype-based diffusion guidance methods with strong early-training performance relative to baseline approaches.}
        \resumeItemListEnd

  \resumeSubHeadingListEnd

%----------- INDUSTRY EXPERIENCE -----------

\section{Industry Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

    \resumeCompanyHeading
      {Novus}{Istanbul, Turkey}
      \resumeRoleHeading
        {Chief Research Officer}{Mar 2024 -- Aug 2024}
      \resumeItemListStart
          \resumeItem{Led research direction for large language model systems and agentic AI applications.}
          \resumeItem{Directed multilingual and low-resource language initiatives spanning model development and evaluation.}
      \resumeItemListEnd

      \resumeRoleHeading
        {Machine Learning Engineer}{Nov 2021 -- Mar 2024}
      \resumeItemListStart
          \resumeItem{Built production-scale Turkish language models and LLM systems using open-source models, supervised fine-tuning, retrieval-augmented generation, and vLLM-based inference backends.}
          \resumeItem{Developed end-to-end ML infrastructure and applications for deployed language technology products.}
      \resumeItemListEnd
    \resumeSubheading
      {Gama Energy}{Istanbul, Turkey}
      {Data Scientist}{Sep 2021 -- Feb 2022}
        \resumeItemListStart
            \resumeItem{Developed automated machine learning pipelines for regression and classification tasks in energy-market settings.}
            \resumeItem{Provided statistical analyses of market drivers and decision-support insights across multiple energy products.}
        \resumeItemListEnd
        
    \resumeSubheading
      {Towards Data Science}{}
      {Technical Writer}{Sep 2021 -- Feb 2022}
        \resumeItemListStart
            \resumeItem{\href{https://taha-huraibb99.medium.com/diffusion-models-demystified-88a25b0bd35a}{\color{blue}Diffusion Models Demystified}}
            \resumeItem{\href{https://towardsdatascience.com/the-essence-of-rnns-44dfb4107a47}{\color{blue}The Essence of RNNs}}
            \resumeItem{\href{https://towardsdatascience.com/nlp-with-cnns-a6aa743bdc1e}{\color{blue}NLP with CNNs}}
            \resumeItem{\href{https://towardsdatascience.com/an-introduction-to-linear-algebra-for-deep-learning-c1b72de78543}{\color{blue}An Introduction to Linear Algebra for Deep Learning}}
        \resumeItemListEnd
  \resumeSubHeadingListEnd





%----------- PUBLICATIONS -----------

\section{Publications}
    \vspace{3pt}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\textbf{Independent-Component-Based Encoding Models of Brain Activity During Story Comprehension}}{}

          \resumeItemListStart
            \resumeItem{K. Hari, \textbf{T. Binhuraib}, J. Li, C. Shain, and A. A. Ivanova. \emph{Independent-Component-Based Encoding Models of Brain Activity During Story Comprehension}. arXiv:2604.24942, 2026. $|$ \href{https://arxiv.org/abs/2604.24942}{\color{blue}Paper}}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{LITcoder: A General-Purpose Library for Building and Comparing Encoding Models}}{}
        
          \resumeItemListStart
            \resumeItem{\textbf{T. Binhuraib}, R. Gao, and A. A. Ivanova. \emph{LITcoder: A General-Purpose Library for Building and Comparing Encoding Models}. NeurIPS DBM 2025 (Accepted). $|$ \href{https://litcoder-brain.github.io/}{\color{blue}Project Page}}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{From Language to Cognition: How LLMs Outgrow the Human Language Network}}{}

          \resumeItemListStart
            \resumeItem{B. AlKhamissi, G. Tuckute, Y. Tang, \textbf{T. Binhuraib}, A. Bosselut, and M. Schrimpf. \emph{From Language to Cognition: How LLMs Outgrow the Human Language Network}. EMNLP 2025 (Oral). $|$ \href{https://aclanthology.org/2025.emnlp-main.1237.pdf}{\color{blue}Paper}}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{TopoLM: brain-like spatio-functional organization in a topographic language model}}{}

          \resumeItemListStart
            \resumeItem{N. Rathi, J. Mehrer, B. AlKhamissi, \textbf{T. Binhuraib}, N. M. Blauch, and M. Schrimpf. \emph{TopoLM: brain-like spatio-functional organization in a topographic language model}. ICLR 2025 (Oral). $|$ \href{https://arxiv.org/pdf/2410.11516}{\color{blue}Paper}}
          \resumeItemListEnd

      \resumeProjectHeading
        {\textbf{Topoformer: brain-like topographic organization in Transformer language models through spatial querying and reweighting}}{}

          \resumeItemListStart
            \resumeItem{\textbf{T. Binhuraib}, G. Tuckute, and N. M. Blauch. \emph{Topoformer: brain-like topographic organization in Transformer language models through spatial querying and reweighting}. ICLR Re-Align 2024. $|$ \href{https://arxiv.org/abs/2510.18745}{\color{blue}Paper}}
          \resumeItemListEnd
          
      \resumeProjectHeading
        {\textbf{Protodiffusion: classifier-free diffusion guidance with prototype learning}}{}
        
          \resumeItemListStart
            \resumeItem{G. Baykal, H. F. Karagoz, \textbf{T. Binhuraib}, and G. Unal. \emph{Protodiffusion: classifier-free diffusion guidance with prototype learning}. ACML 2023. $|$ \href{https://proceedings.mlr.press/v222/baykal24a/baykal24a.pdf}{\color{blue}Paper}}
          \resumeItemListEnd
      
    \resumeSubHeadingListEnd

%----------- TEACHING -----------

\section{Teaching}
  \vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Teaching Assistant, PSYC 2760: Human Language Processing}{Fall 2025}
        \resumeItemListStart
            \resumeItem{Teaching assistant for undergraduate coursework in human language processing.}
        \resumeItemListEnd

    \resumeSubheading
      {Georgia Institute of Technology}{Atlanta, GA}
      {Teaching Assistant, PSYC 2760: Human Language Processing}{Fall 2024}
        \resumeItemListStart
            \resumeItem{Supported instruction and student learning in human language processing.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
        \textbf{Programming:}{ Python, C, C++, Rust, SQL, Go} \\ \vspace{3pt}
        
        \textbf{Technologies:}{ Git, Docker, AWS, Google Cloud, Azure, vLLM} \\ \vspace{3pt}

        \textbf{Web Development:}{ Flask, Django, FastAPI} \\ \vspace{3pt}
        \textbf{Machine Learning:}{ Scikit-learn, PyTorch, TensorFlow, JAX, Transformers (Hugging Face)} \\ \vspace{3pt}

        \textbf{Languages:}{ Arabic (Native), English (Native), Turkish (Native)}
        
        % \textbf{Frameworks}{: X, X, X} \\
        % \textbf{Developer Tools}{: X, X, X} \\
        % \textbf{Libraries}{: X, X, X} \\
        % \textbf{Applications}{: X, X, X}
    }}
  \resumeSubHeadingListEnd



% %----------- RELEVANT COURSEWORK -----------

% \section{Relevant Coursework}
%   \vspace{2pt}
%   \resumeSubHeadingListStart
%     \small{\item{
%         \textbf{Coursework:}{ Deep Learning (graduate-level course), Learn from Data, Analysis
% of Algorithms I \& II, Data Structures, Probability \& Statistics, Object-Oriented Programming, Artificial Intelligence, Discrete Mathematics, Database Systems} \\ \vspace{3pt}
%     }}
%   \resumeSubHeadingListEnd



% %----------- CERTIFICATES -----------

% % \section{Certificates}
%   % \resumeSubHeadingListStart
    
%     % \resumeOrganizationHeading
%       % {Procter \& Gamble VIA Certificate Program}{Feb 2022}{Business Skills, Data and Digital Skills, Project Management and Personal Productivity}
    
%   % \resumeSubHeadingListEnd



% %----------- ORGANIZATIONS -----------

% % \section{Organizations}
%   % \resumeSubHeadingListStart
    
%     % \resumeOrganizationHeading
%       % {Institute of Electrical and Electronics Engineers (IEEE)}{Feb 2022 -- Present}{Student Member}
    
%   % \resumeSubHeadingListEnd



% %----------- HOBBIES -----------

% % \section{Hobbies}
%   % \resumeSubHeadingListStart
%     % \small{\item{Swimming, Fitness, Eight-ball}}
%   % \resumeSubHeadingListEnd



% %----------- REFERENCES -----------

% % \section{References}
%   % \resumeSubHeadingListStart
    
%   % \resumeSubHeadingListEnd



% %-------------------------------------------
\end{document}
